Is high social class always beneficial for survival? A study of northern Sweden 1801--2013 \footnote{Short; "Is high social class beneficial for survival?"}

### 2018-09-29 future.Rmd
Tab for old

fittold <- coxph(Surv(enter, exit, event) ~ hisclass * period * sex + civst + urban, data = vb2)
drold <- drop1(fittold, test = "Chisq")
```

@@

```{r hazcalw2}
nper <- length(labb)
his <- levels(vb1$hisclass)
nhis <- length(his)
##
resm <- matrix(0, nrow = nhis, ncol = nper)
for (i in 1:nper){
    dat <- vb2[vb2$sex == "male" & vb2$period == labb[i], ]
    dat$wght <- getWeights(dat)
    fit <- coxph(Surv(enter, exit, event) ~ strata(hisclass), weights = wght, data = dat)
    resm[, i] <- summary(survfit(fit), rmean = 100)$table[, "*rmean"]
}
##
resw <- matrix(0, nrow = nhis, ncol = nper)
for (i in 1:nper){
    dat <- vb2[vb2$sex == "female" & vb2$period == labb[i], ]
    dat$wght <- getWeights(dat)
    fit <- coxph(Surv(enter, exit, event) ~ strata(hisclass), weights = wght, data = dat)
    resw[, i] <- summary(survfit(fit), rmean = 100)$table[, "*rmean"]
}

>>>>

##fittold <- coxph(Surv(enter, exit, event) ~ hisclass * period * sex ##+ civst + urban, data = vb2)
fittold <- tpchreg(event ~ offset(log(exposure)) + age + hisclass * period * sex + civst + urban, cuts = 65:100, data = vb2Tab)
drold <- drop1(fittold, test = "Chisq")
```

@@

```{r hazcalw2}
nper <- length(labb)
his <- levels(vb2Tab$hisclass)
nhis <- length(his)
##
resm <- matrix(0, nrow = nhis, ncol = nper)
for (i in 1:nper){
    dat <- vb2Tab[vb2Tab$sex == "male" & vb2Tab$period == labb[i], ]
    dat$wght <- getWeights(dat)
    for (j in seq_along(his)){
        fit <- tpchreg(event ~ offset(log(exposure)) + age, 
                       cuts = 65:100, 
                       data = dat[dat$hisclass == his[i], ])
        haz <- c(0, fit$hazards, fit$hazards[length(fit$hazards)])
        resm[j, i] <- mpch(levels = haz, cuts = 65:100)
    }
    ##fit <- coxph(Surv(enter, exit, event) ~ strata(hisclass), weights = wght, data = dat)
    ##resm[, i] <- summary(survfit(fit), rmean = 100)$table[, "*rmean"]
}
##
resw <- matrix(0, nrow = nhis, ncol = nper)
for (i in 1:nper){
    dat <- vb2Tab[vb2Tab$sex == "female" & vb2Tab$period == labb[i], ]
    dat$wght <- getWeights(dat)
        for (j in seq_along(his)){
        fit <- tpchreg(event ~ offset(log(exposure)) + age, 
                       cuts = 65:100, 
                       data = dat[dat$hisclass == his[i], ])
        haz <- c(0, fit$hazards, fit$hazards[length(fit$hazards)])
        resw[j, i] <- mpch(levels = haz, cuts = 65:100)
    }

    ##fit <- coxph(Surv(enter, exit, event) ~ strata(hisclass), weights = wght, data = dat)
    ##resw[, i] <- summary(survfit(fit), rmean = 100)$table[, "*rmean"]
}
